% !TEX root = ./resume.tex

\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
% \fancyfoot[C]{\thepage} % Add page numbers at the center of the footer
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\setlength{\footskip}{13.59999pt}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated PDF is machine-readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeEducationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small#4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%

\begin{document}

%---------- HEADING ----------

\begin{center}
  \textbf{\Huge Muhammad Ukasha} \\ \vspace{3pt}
  \small
  \faMobile \hspace{.5pt} \href{tel:923004761002}{+92 306 025 5284}
  $|$
  \faAt \hspace{.5pt} \href{mailto:mukasha.cse@gmail.com}{mukasha.cse@gmail.com}
  $|$
  \faLinkedinSquare \hspace{.5pt} \href{www.linkedin.com/in/MUkasha09}{LinkedIn}
  $|$
  \faGithub \hspace{.5pt} \href{https://github.com/MUkasha09}{GitHub}
  $|$
  \faMapMarker \hspace{.5pt} {Mian Channu, Pakistan}
\end{center}


%----------- EDUCATION -----------

\section{Education}
\vspace{3pt}
\resumeSubHeadingListStart

\resumeEducationHeading
{The Islamia University of Bahawalpur}{Bahawalpur, Pakistan}
{Bachelor of Science in Computer Systems Engineering; \textbf{CGPA: 3.53/4.00}}{Sep 2021 \textbf{--} Present}

\resumeSubHeadingListEnd

%----------- SKILLS -----------

\section{Skills}
\vspace{2pt}

\resumeSubHeadingListStart
\small{\item{
    \textbf{Languages:} Python, C/C++, SQL \\ \vspace{3pt}
    \textbf{Machine Learning:} scikit-learn, XGBoost, LightGBM, pandas, NumPy \\ \vspace{3pt}
    \textbf{Deep Learning:} TensorFlow, Keras, PyTorch, CNNs, RNNs, LSTMs \\ \vspace{3pt}
    \textbf{Natural Language Processing:} NLTK, spaCy, Hugging Face Transformers, TextBlob, BERT, GPT \\ \vspace{3pt}
    \textbf{Computer Vision:} OpenCV, Image Preprocessing, Data Augmentation \\ \vspace{3pt}
    \textbf{Model Operations:} Model Evaluation, Hyperparameter Tuning, Cross-Validation, Grid Search \\ \vspace{3pt}
    \textbf{Tools \& Platforms:} Jupyter Notebook, Google Colab, Kaggle, Git, GitHub, Weights & Biases \\ \vspace{3pt}
    \textbf{Research & Methodologies:} Sentiment Analysis, Text Classification, Transfer Learning, Prompt Engineering
}}
\resumeSubHeadingListEnd

%----------- EXPERIENCE -----------

\section{Experience}
\vspace{3pt}
\resumeSubHeadingListStart
\resumeSubheading
{Bayer}{Remote}
{Data Analyst}{Jun 2024 -- Sep 2024}
\resumeItemListStart
\resumeItem{
Analyzed agricultural and market datasets to extract actionable insights supporting Bayer’s R\&D and product strategy teams.}
\resumeItem{
Built interactive dashboards and data pipelines using Python (pandas, matplotlib), SQL, and Power BI to monitor crop performance metrics.}
\resumeItem{
Automated data cleansing and transformation workflows, reducing manual reporting time by 50\%.}
\resumeItem{
Collaborated with cross-functional teams to design custom KPIs, ensuring better data-driven decision-making.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
\resumeSubheading
{Freelance Project}{Remote}
{Deep Learning Engineer – Leaf Disease Detection System}{Sep 2024 -- Apr 2025}
\resumeItemListStart
\resumeItem{
Developed a convolutional neural network (CNN)-based model using PyTorch to classify plant leaf diseases from image data with 92\% accuracy.}
\resumeItem{
Built a custom dataset pipeline for image preprocessing, augmentation, and training with real-world agricultural data.}
\resumeItem{
Integrated the model into a user-facing web interface with real-time prediction and visualization using Flask and OpenCV.}
\resumeItem{
Deployed the solution on cloud infrastructure with model logging and result tracking via Weights \& Biases.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%----------- Projects -----------
\section{Projects}
\vspace{3pt}
\resumeSubHeadingListStart

\resumeSubheading
{Sentiment Analysis using Deep Learning}{Final Year Project}
{NLP Engineer}{Sep 2024 -- June 2025}
\resumeItemListStart
\resumeItem{
Built and compared multiple NLP models (Naive Bayes, LSTM, BERT) to classify sentiments from social media text data.}
\resumeItem{
Preprocessed large-scale datasets using NLTK and spaCy, and implemented tokenization, lemmatization, and vectorization techniques.}
\resumeItem{
Evaluated models on accuracy, F1-score, and training time; BERT outperformed others with 93\% F1-score.}
\resumeItem{
Documented experimental findings and performance benchmarks as part of the university's final year capstone requirement.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%----------- AWARDS & ACHIEVEMENTS -----------

\section{Awards \& Achievements}
\vspace{2pt}
\resumeSubHeadingListStart

\resumeItem{
\textbf{Leaf Disease Detection System – Deployed AI Solution:} Successfully built and deployed a deep learning model using CNNs for plant disease classification. Integrated the model into a user-facing web application to assist farmers with real-time diagnosis and decision-making.}
\resumeItemListEnd

\resumeSubHeadingListEnd
\end{document}
